Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-09-06 doc/manuscript/manuscript.Rmd
updte collection

Several of the isolates used for this study were collected and reported in previous studies and were collected using the same methods [@otto-hanson2011variation].
Broadly, isolates were collected from two sources, white mold screening nurseries (wmn) or producer fields.
The white mold screening nurseries were 5m x 10m in size and maintained without applying fungicides to observe natural incidence of white mold.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the growing season [@steadman2003identification; @steadman2004identification; @steadman2005identification; @steadman2006identification; @otto2007identification; @otto2008identification; @mccoy2009use].
Sampling was carried out by collecting diseased tissue in zig-zag transects across field plots. 
Because sampling depended on disease incidence, the number of samples isolated varied from year to year.
Although the nursery locations were the same over sampling years, sampling plots within a location varied for sampling years.

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or wmn in 11 states of the United States of America, Mexico, France, and Australia (Table \@ref(tab:isolate-table)). 
After collection, the isolates were stored in petri plates lined with filter paper, then stored at $20^{\circ}$F or -$4^{\circ}$C. 
Sclerotia were triple rinsed with (i) 50% Clorox bleach/50% double-distilled (dd)H2O solution for 3 min, (ii) ddH2O rinse for 3 min, and (iii) final ddH2O rinse for 3 min, then plated on water agar plates (16g of Bacto agar per liter of ddH2O), with four to five sclerotia of each isolate separated on each plate and stored on the bench top at room temperature for 5 to 6 days An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH2O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

@@

Prior to DNA extraction, isolates were grown on PDA and plugs were subsequently transferred to Potato Dextrose Broth (PDB) where they were grown until there was significant mycelial growth, but before the mycelial mat became solidified (4--5 days).
Mycelial was collected in a buchner funnel, agar plugs removed, lyophilized and pulverized manually in whirl-pak bags. 
Lyophilized mycelia was then stored in microcentrifuge tubes at -$20^{\circ}$C until needed for DNA extraction.
DNA from 25mg of pulverized mycelia was purified using a phenol-chloroform extraction method followed by alcohol precipitation, suspending the DNA in 200$\mu$l TE [@sambrook1989molecular].
Suspended DNA was stored at $4^{\circ}$C until genotyping.

>>>>

Several of the isolates used for this study were collected as reported in previous studies using the same methods [@otto-hanson2011variation].
Broadly, isolates were collected from two sources: white mold screening nurseries (wmn) or producer fields.
<!-- SEE: Insect or weed control? -->
White mold screening nurseries were 5m x 10m in size and maintained without application of fungicides to observe natural incidence of white mold.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the growing season [@steadman2003identification; @steadman2004identification; @steadman2005identification; @steadman2006identification; @otto2007identification; @otto2008identification; @mccoy2009use].

Sampling was carried out by collecting sclerotia from diseased tissue in zig-zag transects across field plots. 
Because sampling depended on disease incidence, the number of samples isolated varied from year to year.
Although the nursery locations were the same over sampling years, sampling plots within a location varied for sampling years.

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or wmn in 11 states of the United States of America, Mexico, France, and Australia (Table \@ref(tab:isolate-table)). 
After collection, sclerotia were stored in Petri plates lined with filter paper, then stored at $20~^{\circ}$F or -$4~^{\circ}$C. 
Sclerotia were surface-sterilized with 50% sodium hypochlorite (at least 6% NaOCL, The Clorox Company, Oakland, CA) solution for 3 min, and double rinsed with ddH$_2$O 3 min.
The sterilized sclerotia were then plated on water agar plates (16g of Bacto agar per liter of ddH$_2$O), with four to five sclerotia of each isolate separated on each plate and stored on the counter top at room temperature for 5 to 6 days. 
An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH$_2$O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

@@

Prior to DNA extraction, isolates were grown on PDA and plugs were subsequently transferred to Potato Dextrose Broth (PDB) where they were grown until there was significant mycelial growth, but before the mycelial mat became solidified (4--5 days).
Mycelial was collected in a buchner funnel, agar plugs removed, lyophilized and pulverized manually in whirl-pak bags. 
Lyophilized mycelia was then stored in microcentrifuge tubes at -$20~^{\circ}$C until needed for DNA extraction.
DNA from 25mg of pulverized mycelia was purified using a phenol-chloroform extraction method followed by alcohol precipitation, suspending the DNA in 200$\mu$l TE [@sambrook1989molecular].
Suspended DNA was stored at $4~^{\circ}$C until genotyping.
